---
output: pdf_document
fontsize: 12pt
---
\pagenumbering{gobble}
```{r, include=FALSE}
source("data prep.R")
```


```{r echo = FALSE}

#Change 1 to i when ready to execute

district <- results_both$Dist[i]
# intakes <- results_both$Intakes[i]
accepted <- results_both$`Not Rejected`[i]

# intake_type <-  as.data.frame(results_both$`Intake Case Types`[i])
accepted_type <- as.data.frame(results_both$`Non-rejected Case Types`[i]) %>%
  rename(Cases = Intakes)

Avg_Pov <- results_both$Avg_Poverty[i]
Vets <- results_both$Vets[i]
COVID <- results_both$COVID[i]
DV <- results_both$DV[i]
Avg_Age <- results_both$`Avg Age`[i]
Clients_w_Children <- results_both$`Clients with Children`[i]
Total_Children <- results_both$`Total Children`[i]
Total_HH_size <- results_both$`Total HH size`[i]
intakes <- results_both$Intakes[i]

```

# Texas RioGrande Legal Aid (TRLA) services for `r district` in 2020

## TRLA completed `r accepted` cases in your district in 2020.

Case types and counts:
`r knitr::kable(accepted_type)`

Of the clients we served in your district:

- `r COVID` clients disclosed that they were affected by COVID-19.

- `r Clients_w_Children` clients had children.

- On average, clients were at `r Avg_Pov` percent of the federal poverty level.

  - For a family of 4, the federal poverty level is $26,200.



```{r, echo = FALSE}

# Number of intakes #
# Number of cases closed #
# Case types (intake)
# Case types (closed)
# Average % poverty level #
# Approx number of veterans #
# Approx number affected by COVID #
# Number involving DV #
# Average age at intake #
# Number of clients with children #
# Number of children #


```

